---
title: "Developing Data Products Final Project Presentation"
author: "Saad Mahmood"
date: "18 November 2018"
output: 
  revealjs::revealjs_presentation:
    transition: zoom 
    theme: moon
    center: true
---

## App Overview

* The application lets you observe global surface temperature changes over the years 1880-2018.
* Data was gathered by NASA exploring surface temperature change from 1880 - 2018.
* The code is divided in two main files: *ui.R* and *server.R*
* *ui.R* is where user inputs are taken and plots are shown.
* *server.R* is where user inputs and processed and the plots are gene  rated.


## Workings of ui.R

* It has a header Panel with the title
* A sidebar panel with the following inputs, a checkbox and a range slider.
```{r eval=FALSE}
    checkboxInput(inputId = "smoother", 
                  "Add A Smoother to Observe Trend", TRUE)
    sliderInput(inputId = "rangeYears", 
                label = "Choose a range of years", 
                value = c(randYear, randYear2),
                min = minYear, 
                max = maxYear,
                dragRange = TRUE
    )
```
* Finally, it has a main panel which shows all the plots

## Workings of server.R
* It uses user inputs as taken from ui.R and uses them to generate a plot.
* The plot is a ggplot object of the temperature changes for each month over the range of years provided by the user.
* It has the following code to add a smoother to the ggplot object
```{r eval=FALSE}
if (input$smoother) {
      g <- g + geom_smooth(aes(color=Month), show.legend = FALSE)
}
```

## Where to find the project:

* The project is hosted on shiny apps at the following link: 
* https://ma7mood.shinyapps.io/my-app/
* The source code of the app is published on github at the following link:
* https://github.com/ma7mood/developingDataProducts/tree/master/my-app

